The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201909/CIV_CLQs_20190926.tex
CIV tex/ tidy up

\author[Bercow]
{%The RH John~S.~Bercow, MP, {\it et al.} 
Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},
 Matthew Graham$^{2}$, K. E. Saavik Ford$^{3,4,5}$,  Barry McKernan$^{3,4,5}$   
\newauthor and Daniel Stern$^{6}$ 
\\
% List of institutions
%$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
$^{2}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
$^{3}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
$^{4}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
$^{5}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

@@

\hypersetup{draft}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first `Changing-Look'' quasars at high
redshift.  This is also the first time the changing-look behaviour has
been seen in a high-ionization emission line.
%%
SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
in their observed optical light curves, and subsequent spectroscopy
shows significant changes in the \civ\ broad emission line, with both
line collapse and emergence being displayed in rest-frame timescales
of $\sim$240-1640 days.
%%
Where observed, the profile of the Ly$\alpha$/\nv emission complex
also changes, and there is tentative evidence for changes in the \mgii
line.
%%
Although line measurements from the three quasars show large changes
in the \civ\ line flux-line width plane, the quasars are not seen to
be outliers when considered against the full $z\sim2$ quasar population
in terms of (rest) Equivalent Width and FWHM properties.
%%
We put these observations in context with recent ``state-change''
models, but note that even in their `low-state', the \civ\ CLQs are
above $\sim$10\% in Eddington luminosity.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their
energy output on timescales of weeks to months.  This observation, and
the subsequent mismatch in the expected ``viscous'' timescale, which
for a $\approx$10$^{7}$ M$_{\odot}$ central supermassive black hole
(SMBH) is $\sim$hundreds of years, was noted over 30 years ago
\citep[e.g.][]{Alloin1985}. However, with new photometric light-curve
and repeat spectroscopic data, the desire for a deeper understanding
of AGN accretion disk physics has been recently re-invigorated the
field \citep[e.g.][]{Lawrence2018, Antonucci2018}.

@@

These CLQs have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, observed from optical
spectroscopy. Recent work \citep{Guo2019, Homan2019} report on discoveries
of \mgii Changing-look AGN. However, current CLQ studies have been at
redshifts $z<1$.

@@

@@

  \begin{tabular}{r l   r ll   r r r r}

@@

    Object                           & \multirow{3}{*}{Redshift}  &                       & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date} & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
    R.A. / deg                     &                                         &   {$g$-band}   &                                 &                                  &                                               &  Time           & Spectrum                 & \\
    Decl. / deg                   &                                         &    magnitude   &                                &                                   &                                              &  / seconds    & Plate-FiberID  & \\

@@

    J120544.7+342252.4   & 2.068$\pm$0.0003         &   18.27             &  53498   &  2005-May-08   & SDSS             &  8057                  & 2089-427             & \\
    181.436164                  & 2.071                              &                         &  58538   &  2019-Feb-24    & DBSP            &  1800                  &  ---                      &  Average conditions \\
    +34.381229                 &                                        &                          &  58693   &  2019-Jul-29     & DBSP            &  2400                   &  ---                      &   \\

@@

    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77              &  54553    & 2008-Mar-28     & SDSS           &   4801                    &  2948-614              & \\
    249.720558	                 &  2.186$\pm$0.0007     &                          &  55832    & 2011-Sep-28     & BOSS            &   3600                   &  5201-178            & \\
    +28.452159                 &  2.182                           &                          &  58583    & 2019-Apr-10     & LRIS              &  1800                   &  ---                             & \\

@@

    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                &  56189    & 2012-Sep-19     & BOSS             &  2700                 &   6118-720          & \\
    337.078194                 & 2.222$\pm$0.0004      &                          &  56960    & 2014-Oct-30     & BOSS             &  4500                  &   7582-790          & eBOSS reobservation \\ 
    +22.017478                &                                      &                          &  58693    & 2019-Jul-29       & DBSP             & 2400                   &    ---                        &    \\

@@

    Redshift and redshift errors from SDSS SkyServer for SDSS, BOSS and eBOSS spectra. 
    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and  eBOSS spectra have $\mathcal{R}\sim$2,000.
    DBSP: Double Spectrograph on the Palomar 200-inch telescope.
    LRIS:  Low Resolution Imaging Spectrometer on Keck I 10m telescope.
    %  2019-Feb-24    & DBSP            &  2$\times$900 f
    %  2019-Jul-29     & DBSP            &  2$\times$1200
    %  2019-Apr-10     & LRIS              &  2$\times$900
    %& 2019-Jul-29       & DBSP             & 2$\times$1200
  } 

@@

In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
the \civ\ doublet \citep{Kramida2018}.  The 1548.202 and 1550.774 \AA\
emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
transition, split by total angular momentum $J= 3/2$ and $1/2$,
resulting in energies 64,591 cm$^{-1}$ and 64,484 cm$^{-1}$,
respectively \citep[e.g.][]{Moore1993}. The transition probabilities
of the the 1548 and 1550\AA\ lines are $A_{ki}= 2.65\times10^{8}$ and
2.64$\times10^{8}$ s$^{-1}$.

The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. Using the
\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
Atomic Spectra Database Ionization Energies Form} for ionisation
energies, we note 11.3 eV is the energy required for C~I to dislodge
one electron and become singly-ionised C~II; 24.4 eV is then the
(`additional') energy needed for singly-ionised C~II to dislodge an
additional electron, and become doubly-ionised C~III, and 47.89 eV
(3.519 Ry) is required for doubly-ionised C~III become triply-ionised
\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
itself. This energy corresponds to a thermal temperature of $T
\gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).  \ciii is the
1$s2$2$s$2$p$ $^{3}$P$^{\circ}$ to 1$s^{2}$2$s^{2}$ $^{1}$S transition
(with $J=1\rightarrow0$) resulting in an energy of 52,390.75 cm$^{-1}$ and
a transition probability of $A_{ki} = 1.14\times10^{2}$ s$^{-1}$ \citep{Wiese1996}.

\citet{Wilhite2006} examine the variability of a C~\textsc{iv} sample
of 105 quasars observed at multiple epochs by the Sloan Digital Sky
Survey \citep[SDSS;][]{York2000, Stoughton2002, Abazajian2009}.  They
find a strong correlation between the change in the C~\textsc{iv} line
flux and the change in the line width, but no correlations between the
change in flux and changes in line center and skewness.  These authors
find that the relation between line flux change and line width change
is consistent with a model in which a broad line base varies with
greater amplitude than the line core. The C~\textsc{iv} lines in these
high-luminosity quasars appear to be less responsive to continuum
variations than those in lower luminosity AGN.  \citet{Wilhite2006}
find no evidence for variability of the well known blueshift of the
C~\textsc{iv} line with respect to the low-ionization
Mg~\textsc{ii}$\lambda$2798 line in the highest flux objects.

\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$ SDSS
quasars, concentrating on the properties of the \civ\ emission
line. We consider two well-known effects involving the \civ\ emission
line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
the BEff) and the blueshifting of the peak of \civ\ emission with
respect to the systemic redshift. These authors conclude that these
two \civ\ parameters (EQW and blueshift) are capturing an important
trade-off between ``disk'' and ``wind'' components in the disk-wind
model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
Proga2000}, with one dominating over the other depending on the shape
of the SED \citep[][strong \civ\ EQW indicates a more ionizing SED and
large \civ\ blueshift indicating a less ionizing SED ]{Leighly2004b}.

The Sloan Digital Sky Survey Reverberation Mapping Project
\cite[SDSS-RM; ][]{Shen2015} has a monitored $\sim$350 quasars with
\civ. Noting the biases associated with \civ Emission Line Properties
\citep[e.g. increasing systematic offsets with decreasing
signal-to-noise][]{Denney2016}, \citet{Grier2019} report report
significant time delays between the continuum and the CIV 1549
emission line in 52 quasars, and investigate the \civ
radius-luminosity relationship.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
Sloan Digital Sky Survey Reverberation Mapping project to investigate
the dependence of the blueshift of \civ\ relative to \mgii on quasar
properties. We confirm that high-blueshift sources tend to have low
\civ\ equivalent widths (EWs), and that the low-EW sources span a range
of blueshift. Other high-ionization lines, such as He II, also show
similar blueshift properties. The ratio of the line width (measured as
both the full width at half maximum and the velocity dispersion) of
\civ\ to that of \mgii increases with blueshift. Quasar variability
enhances the connection between the \civ\ blueshift and quasar
properties (e.g., EW). The variability of the \mgii line center (i.e.,
the wavelength that bisects the cumulative line flux) increases with
blueshift. In contrast, the C IV line center shows weaker variability
at the extreme blueshifts. Quasars with the high-blueshift \civ\ lines
tend to have less variable continuum emission, when controlling for
EW, luminosity, and redshift. Our results support the scenario that
high-blueshift sources tend to have large Eddington ratios.
Therefore, according to this study, the \civ\ or \heii\ EW is not an
accurate indicator of the Eddington ratio or quasar SED.
Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}. 
\citet{Dyer2019} provide a detailed analysis of 340 quasars at high-redshift
($1.62<z<3.30$) from the SDSS-RM project, which we will compare our
results to.

%%   P a p e r    O v e r v i e w
The purpose of this paper is, for the first time, to access and 
report on the Changing-Look quasar phenomenon at high, 
$z>2$ redshift. By doing so, we move from the low-ionization 
energy Balmer emission line series to the high-ionization emission 
lines, in particular \civ\ $\lambda$1549.

This paper is organised as follows. In Section 2, we describe our
sample selection, catalogs and observational data sets.  In Section 3,
we present the high-$z$ quasars and report the line properties for the
quasars at the observed epochs.  We give a very brief theoretical
discussion in Section 4. We present our Conclusions in Section 5.  We
report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
Fukugita1996} unless otherwise stated explicitly. For the WISE bands,
$m_{\rm AB} = m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1
at 3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively
\citep{Cutri2011}.
We adopt a flat $\Lambda$CDM cosmology with $\Omega_{\Lambda} = 0.73$,
$\Omega_{\rm M} = 0.27$, and $h = 0.71$ in order to be consistent with
\citet{Hamann2017}. As a guide this cosmology has a $z=2.000$
comoving radial distance of 5244.3 Mpc, a $\sim$1.25\% difference
compared to 5179.0 Mpc from $\Omega_{\Lambda} = 0.70$, $\Omega_{\rm M}
= 0.30$, and $h = 0.70$ that is used in \citet{Shen2011}.

>>>>

\author[Bercow]
{The RH John~S.~Bercow, MP, {\it et al.} 
%Nicholas~P.~Ross$^{1}$\thanks{E-mail: npross@roe.ac.uk},    
%K. E. Saavik Ford$^{2,3,4}$,  Matthew Graham$^{5}$,  Barry McKernan$^{2,3,4}$,  
%\newauthor Daniel Stern$^{6}$, 
\\
% List of institutions
$^{1}$Speaker's Chair, The House of Commons, London, SW1A 0AA \\
%$^{1}$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, United Kingdom \\
%$^{2}$Department of Science, BMCC, City University of New York, New York, NY 10007, USA \\
%$^{3}$Department of Astrophysics, Rose Center for Earth and Space, American Museum of Natural History, Central Park West at 79th Street, NY 10024, USA \\
%$^{4}$Graduate Center, City University of New York, 365 5th Avenue, New York, NY 10016, USA\\
%$^{5}$Cahill Center for Astronomy and Astrophysics, California Institute of Technology, Mail Code 249/17, 1200 E California Blvd, Pasadena CA 91125, USA\\
%$^{6}$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Drive, Mail Stop 169-221, Pasadena, CA 91109, USA \\
}

@@

\hypersetup{draft}
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
We report on three redshift $z>2$ quasars with dramatic changes in
their \civ\ emission lines, the first `Changing-Look'' quasars at high
redshift.  This is also the first time the changing-look behaviour has
been seen in a high-ionization emissions line.
%%
SDSS J1205+3422, J1638+2827 and J2228+2201 show interesting behaviour
in their observed optical light curves, and subsequent spectroscopy
shows significant changes in the \civ\ broad emission line, with both
line collapse and emergence being displayed in rest-frame timescales
of $\sim$240-1640 days.
%%
Where observed, the profile of the Ly$\alpha$/\nv emission complex
also changes, and there is tentative evidence for changes in the \mgii
line.
%%
Although line measurements from the three quasars show large changes
in the \civ\ line flux-line width plane, the quasars are not seen to
be outliers when considered against the full $z>2$ quasar population
in terms of (rest) Equivalent Width and FWHM properties.
%%
We put these observations in context with recent ``state-change''
models, but note that even in their `low-state', the \civ\ CLQs are
above $\sim10\%$ in Eddington luminosity.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their
energy output on timescales of weeks to months.  This observation, and
the subsequent mismatch in the expected ``viscous'' timescale, which
for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was
noted over 30 years ago \citep[e.g.][]{Alloin1985}. However, with new
photometric light-curve and repeat spectroscopic data, the desire for
a deeper understanding of AGN accretion disk physics has been recently
re-invigorated the field \citep[e.g.][]{Lawrence2018, Antonucci2018}.

@@

These CLQs have primarily been defined according to the
(recombination) Balmer emission line properties with particular
attention paid to the H$\beta$ emission line, usually observed from
optical spectroscopy.  As such, current CLQ studies have been at
redshifts $z<1$.

@@

In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
the \civ\ doublet \citep{Kramida2018}. The ground state of carbon is
1$s^2$ 2$s^2$ 2$p^2$.  Using the
\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
Atomic Spectra Database Ionization Energies Form} for ionisation
energies, we note 11.3 eV is the energy required for C~I to dislodge
one electron and become singly-ionised C~II; 24.4 eV is then the
(`additional') energy needed for singly-ionised C~II to dislodge an
additional electron, and become doubly-ionised C~III, and 47.89 eV
(3.519 Ry) is required for doubly-ionised C~III become triply-ionised
\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
itself. The 1548.202 and 1550.774 \AA\ emission doublet is created by
the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition with energies 64,484
cm$^{-1}$ and 64,591 cm$^{-1}$ \citep[e.g.][]{Moore1993}.

\citet{Wilhite2006} examine
the variability of a C~\textsc{iv} sample of 105 quasars observed at
multiple epochs by the SDSS.  They find a strong correlation between
the change in the C~\textsc{iv} line flux and the change in the line
width, but no correlations between the change in flux and changes in
line center and skewness.  These authors find that the relation
between line flux change and line width change is consistent with a
model in which a broad line base varies with greater amplitude than
the line core. The C~\textsc{iv} lines in these high-luminosity
quasars appear to be less responsive to continuum variations than
those in lower luminosity AGN.  \citet{Wilhite2006} find no evidence
for variability of the well known blueshift of the C~\textsc{iv} line
with respect to the low-ionization Mg~\textsc{ii}$\lambda$2798 line in
the highest flux objects.

\citet{Richards2011} explored the BEL region in over 30,000 $z > 1.54$ SDSS
quasars, concentrating on the properties of the \civ\ emission
line. We consider two well-known effects involving the \civ\ emission
line: the anti-correlation between the \civ\ EQW and luminosity (i.e.,
the BEff) and the blueshifting of the peak of \civ\ emission with
respect to the systemic redshift. These authors conclude that these
two \civ\ parameters (EQW and blueshift) are capturing an important
trade-off between ``disk'' and ``wind'' components in the disk-wind
model of accretion disks \citep[e.g.,][]{Murray1995, Elvis2000,
Proga2000}.  with one dominating over the other depending on the shape
of the SED \citep[][strong \civ\ EQW indicates a more ionizing SED and
large \civ\ blueshift indicating a less ionizing SED]{Leighly2004b}.

The Sloan Digital Sky Survey Reverberation Mapping Project
\cite[(SDSS-RM)][]{Shen2015} has a monitored $\sim$350 quasars with
\civ. Noting the biases associated with \civ Emission Line Properties
\citep[e.g. increasing systematic offsets with decreasing
signal-to-noise][]{Denney2016}, \citet{Grier2019} report report
significant time delays between the continuum and the CIV 1549
emission line in 52 quasars, and investigate the \civ
radius-luminosity relationship.

\citet{Sun2018} use the multi-epoch spectra of 362 quasars from the
Sloan Digital Sky Survey Reverberation Mapping project to investigate
the dependence of the blueshift of \civ\ relative to \mgii on quasar
properties. We confirm that high-blueshift sources tend to have low
\civ\ equivalent widths (EWs), and that the low-EW sources span a range
of blueshift. Other high-ionization lines, such as He II, also show
similar blueshift properties. The ratio of the line width (measured as
both the full width at half maximum and the velocity dispersion) of
\civ\ to that of \mgii increases with blueshift. Quasar variability
enhances the connection between the \civ\ blueshift and quasar
properties (e.g., EW). The variability of the \mgii line center (i.e.,
the wavelength that bisects the cumulative line flux) increases with
blueshift. In contrast, the C IV line center shows weaker variability
at the extreme blueshifts. Quasars with the high-blueshift \civ\ lines
tend to have less variable continuum emission, when controlling for
EW, luminosity, and redshift. Our results support the scenario that
high-blueshift sources tend to have large Eddington ratios.
Therefore, according to this study, the \civ\ or \heii\ EW is not an
accurate indicator of the Eddington ratio or quasar SED.
%%
Recent investigations also include \citet{Meyer2019} and \citet{Doan2019}.

The purpose of this paper is, for the first time, to access and 
report on the Changing-Look quasar phenomenon at high, 
$z>2$ redshift. By doing so, we move from the low-ionization 
energy Balmer emission line series to the high-ionization emission 
lines, in particular \civ\ $\lambda$1549.

This paper is organised as follows. In Section 2, we describe our
sample selection, catalogs and observational data sets.  In Section 3,
we present the high-$z$ quasars and report the line properties for the
quasars at the observed epochs.  We give a very brief theoretical
discussion in Section 4. We present our Conclusions in Section 5.  We
report all magnitudes on the AB zero-point system \citep{Oke_Gunn1983,
Fukugita1996} unless otherwise stated explicitly. For the WISE bands,
$m_{\rm AB} = m_{\rm Vega} + m$ where $m = (2.699, 3.339)$ for WISE W1
at 3.4$\mu$m and WISE W2 at 4.6$\mu$m, respectively
\citep{Cutri2011}. We choose the cosmological parameters
$\Omega_{\Lambda} = 0.7$, $\Omega_{\rm M} = 0.3$, and $h = 0.7$ in
order to be consistent with \citet{Shen2011}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

  \begin{tabular}{r  r  r r r   r r r r}

@@

    Object                         & \multirow{3}{*}{Redshift} & \multirow{3}{*}{$g$-band mag}      & \multirow{3}{*}{MJD} & \multirow{3}{*}{Date}  & \multirow{3}{*}{Instrument}  & Exposure      & SDSS                        & \multirow{3}{*}{Notes} \\
    R.A. / deg                   &                                         &                                                          &                                 &                                   &                                               &  Time           & Spectrum                 & \\
    Decl. / deg                 &                                         &                                                          &                                &                                     &                                              &  / seconds    & Plate-FiberID  & \\

@@

    J120544.7+342252.4  & 2.068$\pm$0.0003          &   18.27             & 53498  &  2005-May-08   & SDSS             & tbd                          & 2089-427             & \\
    181.436164          & 2.071                               & {\bf 17.99?}   & 58538  &  2019-Feb-24    & DBSP            &  2$\times$900    &                               &  Conditions? \\
    +34.381229           &                                        &                          & 58693  &  2019-Jul-29     & DBSP            &  2$\times$1200   &                              &   \\

@@

    J163852.9+282707.7   & 2.185$\pm$0.0004       &   19.77               & 54553 & 2008-Mar-28     & SDSS             & tbd                          &  2948-614              & \\
    249.720558	             &  2.186$\pm$0.0007      &                           & 55832  & 2011-Sep-28     & BOSS            &   3603                  &  5201-178            & \\
    +28.452159             &  2.182                           &                           & 58583 & 2019-Apr-10      & LRIS              &  2$\times$900    &                              & \\

@@

    J222818.7+220102.9   & 2.217$\pm$0.0021      & 19.97                 & 56189 & 2012-Sep-19      & BOSS             &  2702                 &   6118-720          & \\
    337.078194             & 2.222$\pm$0.0004      &                          & 56960 & 2014-Oct-30      & BOSS             & tbd                         &   7582-790          & QSO1-REOBS \\ 
    +22.017478            &                                      &                          & 58693 & 2019-Jul-29        & DBSP              & 2$\times$1200  &                           &    \\

@@

    Exposure times are from the {\tt plate.fits} file.  SDSS, BOSS and
    eBOSS spectra have $\mathcal{R}\sim$2,000.  DBSP is the
    $\mathcal{R}\sim$1,000-10,000 resolution Double Spectrograph for the
    Palomar 200-inch telescope.  LRIS is the Low Resolution Imaging
    Spectrometer on the Keck I 10m telescope.} 

@@

\section{Data}
%% \subsection{Selection/Identification}
{\bf MJG to write a few notes on how the CIV CLQs were identified} 
lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam
porta sodales est, vel cursus risus porta non. Vivamus vel pretium
velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
eu blandit. Donec in lacinia libero.

SDSS J120544.7+342252.4  (hereafter J1205+3422), 
SDSS J163852.93+282707.7 (hereafter J1638+2827) and
SDSS J222818.76+220102.9 (hereafter J2228+2201). 
Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
euismod. Cras vel auctor neque. Nam quis diam risus.

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
  {figures/J1205+3422_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.05cm 0.2cm 0.1cm, clip]
  {figures/J1638+2827_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.0cm  0.2cm 0.1cm, clip]
  {figures/J2228+2201_landscape_20190920.png}
  \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
    SDSS J1205+3422 (top), 
    SDSS J1638+2827 (middle), 
    SDSS J2228+2201 (bottom). 
The light curve data is present in the panels on the left hand side, with the 
spectral epoch observational timings given by the vertical lines. 
The spectra are on the right hand side, with zoom-in's on the Ly$\alpha$-\nv 
complex, the \civ\ line and the \mgii line. 
  }
  \label{fig:civ_clqs}
\end{figure*}
\subsection{Spectra}
An overview of our spectroscopic observations is given in
Table~\ref{tab:obs_notes}.  The spectra are from the SDSS
\citep{Stoughton2002, DR7, Schneider2010}, the SDSS-III Baryon
Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011,
Dawson2013, Smee2013, Alam2015, Paris2017} and the SDSS-IV Extended
Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016,
Abolfathi2018, Paris2018}.  These quasars were targetted via a range of
techniques and algorithms \citep[][]{Richards2002, Ross2012,
Myers2015}.  These data are supplemented by spectra from the Low
Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I}
telescope \citep{Oke1995}.  and the Double Spectrograph (DBSP)
instrument on the Palomar {\it Hale} 5m telescope.

\begin{table*}
\begin{tabular}{ l rrrr rrrr rrrr rrrr rrrr rr|}
\hline
\hline 
Object (MJD)               & $f$1450 & $\alpha_{\rm C IV}$    & $\alpha$    & REW                       & cREW   &  wREW  & FWHM              & cFWHM  &  wFWHM  & $\sigma$     \\
\hline 
J1638+2827 (55832) & 1.4659    & -3.3547             & -4.026$\pm$0.452 & 42.76$\pm$1.96  & 26.72  & 16.03  & 5210$\pm$226 & 4651      & 13444    & 3702          \\
J2228+2201 (56189) & 0.5101    & -1.5931             & -0.657$\pm$0.004 & 42.18$\pm$5.59  &  6.42   & 35.76  & 2994$\pm$620 & 1458      &   7636    & 3002           \\
\hline
\end{tabular}
 \caption{
Measured line values using the methods and catalogue from \citet{Hamann2017}. 
\noindent {\tt f1450} = flux in the uncorrected BOSS spectrum at 1450 \AA\ rest (10$^{-17}$ ergs s$^{-1}$ cm$^{-2}$ \AA$^{-1}$) used to anchor the power law continuum fits beneath \civ\ and \nv , 
                                     e.g., $f_{\lambda} = f_{1450}\, (\lambda /1450{\rm \AA})^{\alpha}$; 
\noindent {\tt $\alpha_{\rm C IV}$} = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) measured from the BOSS spectrum on either side of \civ ; 
\noindent {\tt $\alpha$}                            = power law continuum slope ($f_{\lambda}\propto \lambda^{\alpha}$) between 1350 \AA\ and 2200 \AA\ in the flux corrected BOSS spectrum; 
\noindent {\tt REW} = \civ\ REW (\AA ) from the line profile fit;
\noindent {\tt cREW} = \civ\ REW (\AA ) for the core Gaussian component;
\noindent {\tt wREW} = \civ\ REW (\AA ) for the wing Gaussian component; 
\noindent {\tt FWHM} = \civ\ FWHM (km/s) from the line profile fit; 
\noindent {\tt fwhmc} = \civ\ FWHM (km/s) for the core Gaussian only.
\noindent {\tt fwhmw} = \civ\ FWHM (km/s) for the wing Gaussian only.
\noindent {\tt $\sigma$} = \civ\ velocity dispersion (km/s) measured from the profile fit \citep{Peterson2004}.
Errors were given are 1$\sigma$ uncertainties. 
} 
 \label{tab:Ham17_lines}
\end{table*}

\begin{table*}
\begin{tabular}{ l rrr rrr rrr rrr}
\hline
\hline
  \multicolumn{1}{c}{Object (MJD)} &
  \multicolumn{1}{c}{$M_{\rm I}(z=2)$} &
  \multicolumn{1}{c}{$\log$($L_{\rm Bol} / {\rm erg s}^{-1}$} &
  \multicolumn{1}{c}{$\log(L_{\rm CIV})$} &
  \multicolumn{1}{c}{FWHM} &
  \multicolumn{1}{c}{EW} &
  \multicolumn{1}{c}{$\alpha$} &
  \multicolumn{1}{c}{$\log$BH } &
  \multicolumn{1}{c}{Edd. ratio, \%)} \\
\hline
  J1205+3422 (53498)   & 
  -27.742                      & 47.22$\pm$0.004    &    %46.37$\pm$0.009    & 46.634$\pm$0.004   & 44.896$\pm$0.013 & 
44.896$\pm$0.014     &   5230$\pm$219          & 30.1$\pm$1.21        &  -1.467$\pm$0.076    &  % & 27.59                         & 1118$\pm$133.5 & 
  9.494$\pm$0.036    &  42 \\
%%
 J1638+2827 (54553)   & 
 -26.750                      & 46.17$\pm$0.040    & %45.50$\pm$0.086      & 45.586$\pm$0.040 & 44.449$\pm$0.036   & 
44.449$\pm$0.036    &  4180$\pm$736          & 100.5$\pm$11.9      & -0.137$\pm$0.677    &   % & 4.630                      & 680$\pm$133.5         & 
  8.743$\pm$0.154     & 21  \\
\hline
\hline
\end{tabular}
 \caption{
Measured line values using the methods and catalogue from
\citet{Shen2011}.  $M_{\rm I}(z=2)$ is the Absolute $i$-band magnitude
$K$-corrected to $z = 2$; Bolometric luminosity computed from the
monochromatic luminosity at 1350\AA\ using the spectral fits and
bolometric corrections (BC = 3.81) in \citet{Richards2006b}; Line
luminosity, FWHM, rest-frame equivalent width, and their errors for
the whole \civ\ profile.  Power-law slope $\alpha_{\lambda}$ for the
continuum fit for \civ; Virial BH masses using calibrations of
\citet{VestergaardPeterson2006}.  Eddington ratio computed using the
virial BH mass.
}
 \label{tab:Shen11_lines}
\end{table*}
